---
title: "Case Detection Scenario Main Analysis"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: github_document
keep.md: true
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# CHANGE: Altered import to use local package rather than installing epicR
# into the r environment with renv

# Load local package epicR
devtools::load_all("../epicR")

# Clear environment as want to use library(epicR) below, which will use the
# devtools loaded library, but want to clear any other bits load_all() brought
# in and just work with that package from a "clean slate".
rm(list=ls())
```

```{r}
# CHANGE: Add a timer (will see addition below to print time too)
# Start timer
start.time <- Sys.time()
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
set.seed(333) #333 is the analysis seed
library(epicR)
library(tidyverse)
library(knitr)
library(kableExtra)
```

```{r global settings, echo=FALSE}
record_mode<-c(
    record_mode_none=0,
    record_mode_agent=1,
    record_mode_event=2,
    record_mode_some_event=3)
  
settings <- get_default_settings()
settings$record_mode <- record_mode["record_mode_none"]
# CHANGE: Using fewer agents than original script (50e6) or stated number used
# for publication (100e6)
settings$n_base_agents <- 50e6
lambda=50000 # change WTP threshold here
  
init_session(settings = settings)
input <- init_input()

years_btw_case_detection=3
medication_utility=0.0367
medication_adherence=0.7
smoking_adherence=0.7

other_years_btw_case_detection=5 # other time interval
```

**Global inputs:**

  - Medication adherence is `r medication_adherence`
  - Smoking adherence is `r smoking_adherence`
  - Cost discounting: `r input$values$global_parameters$discount_cost`
  - QALY discounting: `r input$values$global_parameters$discount_qaly`
  - Time horizon: `r input$values$global_parameters$time_horizon`
  - The WTP threshold for NMB is `r format(lambda, scientific = FALSE)`
  
**Case detection inputs:**

  - Case detection occurs at `r years_btw_case_detection` year intervals.
  - An outpatient diagnosis costs `r input$values$cost$cost_outpatient_diagnosis`
  - The utility gain due to symptom relief from treatment is `r medication_utility`

## S1 All patients scenario

All patients are eligible.  The cost of case detection is:

```{r S1 CD costs, echo=FALSE}
costs <- data.frame(t(input$values$diagnosis$case_detection_methods[3,]))
kable(costs) 
```


#### S1NoCD: No Case detection

```{r Inputs s1NoCD, echo=FALSE}
CD_method = "None" # change inputs here
yrs_btw_CD = 3 # change inputs here
min_age = 40 # change inputs here
min_pack_years = 0 # change inputs here
num_symptoms=0 # change inputs here
med_adherence=0.7
smoking_adherence=0.7
time_horizon=20
medication_utility=0.0367 
discount_rate=0.015
```


```{r Run s1NoCD, echo=FALSE}
input$values$diagnosis$years_btw_case_detection <- yrs_btw_CD
input$values$diagnosis$min_cd_age <- min_age
input$values$diagnosis$min_cd_pack_years <- min_pack_years
input$values$diagnosis$min_cd_symptoms <- num_symptoms
input$values$medication$medication_adherence <- med_adherence
input$values$smoking$smoking_cessation_adherence <- smoking_adherence
input$values$global_parameters$time_horizon <- time_horizon
input$values$medication$medication_utility <-c(None=0,SABA=medication_utility, LABA=0,SABA_LABA=0, LAMA=medication_utility, LAMA_SABA=0,
                                        LAMA_LABA=medication_utility, LAMA_LAMA_SABA=0, ICS=0, ICS_SABA=0, ICS_LABA=0, ICS_LABA_SABA=0,
                                        ICS_LAMA=0, ICS_LAMA_SABA=0, ICS_LAMA_LABA=medication_utility, ICS_LAMA_LABA_SABA=0)
input$values$global_parameters$discount_cost <- discount_rate
input$values$global_parameters$discount_qaly <- discount_rate
input$values$cost$cost_case_detection <- input$values$diagnosis$case_detection_methods[3,CD_method]
  
input$values$diagnosis$logit_p_prevalent_diagnosis_by_sex <- cbind(male=c(intercept=1.0543, age=-0.0152, smoking=0.1068, fev1=-0.6146, cough=0.075, phlegm=0.283, wheeze=-0.0275, dyspnea=0.5414, case_detection=input$values$diagnosis$case_detection_methods[1,CD_method]),
female=c(intercept=1.0543-0.1638, age=-0.0152, smoking=0.1068, fev1=-0.6146, cough=0.075, phlegm=0.283, wheeze=-0.0275,   dyspnea=0.5414, case_detection=input$values$diagnosis$case_detection_methods[1,CD_method]))
  
input$values$diagnosis$logit_p_diagnosis_by_sex <- cbind(male=c(intercept=-2, age=-0.0324, smoking=0.3711, fev1=-0.8032,
gpvisits=0.0087, cough=0.208, phlegm=0.4088, wheeze=0.0321, dyspnea=0.722,   case_detection=input$values$diagnosis$case_detection_methods[1,CD_method]), female=c(intercept=-2-0.4873, age=-0.0324, smoking=0.3711, fev1=-0.8032, gpvisits=0.0087, cough=0.208, phlegm=0.4088, wheeze=0.0321, dyspnea=0.722, case_detection=input$values$diagnosis$case_detection_methods[1,CD_method]))
  
input$values$diagnosis$logit_p_overdiagnosis_by_sex <- cbind(male=c(intercept=-5.2169, age=0.0025, smoking=0.6911, gpvisits=0.0075,
cough=0.7264, phlegm=0.7956, wheeze=0.66, dyspnea=0.8798, case_detection=input$values$diagnosis$case_detection_methods[2,CD_method]),
female=c(intercept=-5.2169+0.2597, age=0.0025, smoking=0.6911, gpvisits=0.0075, cough=0.7264, phlegm=0.7956, wheeze=0.66,  dyspnea=0.8798, case_detection=input$values$diagnosis$case_detection_methods[2,CD_method]))
  
run(input = input$values)

inputs <- Cget_inputs()
output <- Cget_output()
output_ex <- Cget_output_ex()

copdPY <- output$cumul_time - output_ex$cumul_non_COPD_time
totalPY <- output$cumul_time

terminate_session()
```


```{r Outputs s1NoCD, echo=FALSE}
base <- data.frame(Scenario="S1NoCD",
                    Agents=output$n_cohort,
                    PatientYears=totalPY,
                    CopdPYs=copdPY,
                    NCaseDetections=output_ex$n_total_case_detection,
                    DiagnosedPYs=output$total_diagnosed_time,
                    OverdiagnosedPYs=sum(output_ex$n_Overdiagnosed_by_ctime_sex))

meds <- output_ex$medication_time_by_class[-5]
meds <- c(meds[1]/totalPY, meds[-1]/copdPY)
names(meds) <- c("SABA","LAMA","LAMALABA","ICSLAMALABA")
meds <- data.frame(t(meds))

exac <- output$total_exac
names(exac) <- c("Mild","Moderate","Severe","VerySevere")
exac <- data.frame(t(exac))

exacPY <- output$total_exac/copdPY
names(exacPY) <- c("MildPY","ModeratePY","SeverePY","VerySeverePY")
exacPY <- data.frame(t(exacPY))

gold<- colSums(output_ex$n_COPD_by_ctime_severity)
names(gold) <- c("NoCOPD","GOLD1","GOLD2","GOLD3","GOLD4")
gold <- data.frame(t(gold))

payoffs <- data.frame(Cost=output$total_cost, CostpAgent=output$total_cost/output$n_cohort,
                      QALY=output$total_qaly, QALYpAgent=output$total_qaly/output$n_cohort)
payoffs$NMB <- (payoffs$QALYpAgent)*lambda - (payoffs$CostpAgent)

s1NoCD <- cbind(base, meds, exac, exacPY, gold, payoffs)
```

```{r save}
write.csv(s1NoCD, "../outputs/s1NoCD_50mil.csv", row.names=FALSE)
```

## Time elapsed

Run time for this notebook:

```{r runtime}
end.time <- Sys.time()
time.taken <- end.time - start.time
time.taken
```
