---
title: "Process Model Results"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  github_document:
    df_print: "kable"
keep.md: true
---

This file processes the model results so they match up as closely as possible to those in the publication.

It aims to produce **Table 3**, **Figure 3** and **Appendix 6**.

```{r, message=FALSE}
# Clear environment before start
rm(list=ls())

# Set save location for figures generated when knit rmd
knitr::opts_chunk$set(fig.path = "../outputs/")

# Load required libraries
library(dplyr)
library(ggplot2)
library(ggpubr)
```

## Define file paths and import files

```{r}
paths <- list(
  # Model results
  s1 = "../outputs/s1.csv",
  sall_3y = "../outputs/sall.csv",
  sall_5y = "../outputs/sall_5y.csv",
  ceplane_3y = "../outputs/ceplane.csv",
  ceplane_5y = "../outputs/ceplane_5y.csv",
  clinical = "../outputs/clinicalresults.csv",

  # Original study results
  paper_tab3 = "../../original_study/tab3.csv",
  original_sall = "../../original_study/sall.csv",
  original_ceplane = "../../original_study/ceplane.csv",

  # Outputs from this .Rmd file
  tab3 = "../outputs/tab3.csv",
  tab3_compare = "../outputs/tab3_compare_to_original.csv",
  fig3 = "../outputs/fig3-1.png",
  apx6 = "../outputs/appendix6-1.png"
)
```

```{r}
s1 <- read.csv(paths$s1)
sall_3y <- read.csv(paths$sall_3y) %>% mutate("Interval" = "3 years")
sall_5y <- read.csv(paths$sall_5y) %>% mutate("Interval" = "5 years")
ceplane_3y <- read.csv(paths$ceplane_3y) %>% mutate("Interval" = "3 years")
ceplane_5y <- read.csv(paths$ceplane_5y) %>% mutate("Interval" = "5 years")
clinical <- read.csv(paths$clinical)

paper_tab3 <- read.csv(paths$paper_tab3)
original_sall <- read.csv(paths$original_sall)
original_ceplane <- read.csv(paths$original_ceplane)
```

## Table 3

Preview the results.

```{r}
rbind(ceplane_3y, ceplane_5y) %>%
  arrange(Scenario)
```

Combine, organise and modify results as per paper.

```{r}
ceplane <- rbind(ceplane_3y, ceplane_5y) %>%
  # Remove scenarios 2 and 3 with no case detection, and scenario 2b
  filter(!(Scenario %in% c("S2NoCD", "S3NoCD", "S2b"))) %>%
  # Remove S1NoCDAvg from 5 years, then set interval of S1NoCDAvg to NA
  filter(!(Scenario == "S1NoCDAvg" & Interval == "5 years")) %>%
  mutate(Interval = ifelse(Scenario == "S1NoCDAvg", NA, Interval)) %>%
  # Remove INMB for S1NoCDAvg
  mutate(INMB = ifelse(Scenario!="S1NoCDAvg", INMB, NA)) %>%
  # Get INMB ranking
  mutate(Ranking = min_rank(desc(INMB)))

ceplane %>% arrange(Scenario)
```

Reformat to match paper.

```{r}
ceplane_pretty <- ceplane %>%
  # Round columns
  mutate(CostpAgentAll = paste0("$", round(CostpAgentAll, 0))) %>%
  mutate(QALYpAgentAll = round(QALYpAgentAll, 3)) %>%
  mutate(ICERAdj = round(ICERAdj, 0)) %>%
  # Create INMB and rank column
  mutate(INMBRank = ifelse(
    Scenario!="S1NoCDAvg",
    paste0(round(INMB, 0), "(", Ranking, ")"),
    NA)) %>%
  # Arrange and relabel the scenarios
  arrange(Scenario) %>%
  mutate(Scenario = recode(Scenario,
                           "S1NoCDAvg" = "S0: No case detection",
                           "S1a" = "(S1a) CDQ ≥ 17 points",
                           "S1b" = "(S1b) Screening spirometry",
                           "S1c" = "(S1c) CDQ + screening spirometry",
                           "S2a" = "(S2a) Screening spirometry",
                           "S3a" = "(S3a) CDQ ≥ 19.5 points",
                           "S3b" = "(S3b) CDQ ≥ 16.5 points",
                           "S3c" = "(S3c) Screening spirometry",
                           "S3d" = "(S3d) CDQ + screening spirometry")) %>%
  # Select, reorder and relabel columns
  select(Scenario, Interval, CostpAgentAll, QALYpAgentAll, ICERAdj, INMBRank) %>%
  rename("Testing interval" = Interval,
         "Costs per patient" = CostpAgentAll,
         "QALYs per patient" = QALYpAgentAll,
         "ICER" = ICERAdj,
         "INMB (ranking)" = INMBRank)

# Save to csv
write.csv(ceplane_pretty, paths$tab3, row.names=FALSE)

# View dataframe
ceplane_pretty
```

### Compare between our results, the paper, and their repository

Prepare our model results...

```{r}
# Prepare sall model results to combine with original table
ceplane_prep <- ceplane %>%
  # Replace S1NoCDAvg with S0
  mutate(Scenario = replace(Scenario, Scenario == "S1NoCDAvg", "S0")) %>%
  # Round columns
  mutate(CostpAgentAll = round(CostpAgentAll, 0)) %>%
  mutate(QALYpAgentAll = round(QALYpAgentAll, 3)) %>%
  mutate(ICERAdj = round(ICERAdj, 0)) %>%
  mutate(INMB = round(INMB, 0)) %>%
  # Select relevant columns
  select(Scenario, Interval, CostpAgentAll, QALYpAgentAll, ICERAdj, INMB, Ranking)
ceplane_prep
```

Prepare results from the paper...

```{r}
# Convert costs to numeric
paper_tab3_prep <- paper_tab3 %>%
  mutate(CostpAgent = readr::parse_number(CostpAgent))
# Append "_paper" to columns (except Scenario and Interval)
icol <- which(names(paper_tab3_prep) %in% c("Scenario", "Interval"))
colnames(paper_tab3_prep)[-icol] <- paste(colnames(paper_tab3_prep)[-icol], "paper", sep = "_")
# Preview dataframe
paper_tab3_prep
```
```{r}
original_ceplane_prep <- original_ceplane %>%
  # Replace "NA" string with actual NaN for the interval
  mutate(Interval = replace(Interval, Interval == "NA", NA_character_)) %>%
  # Remove scenarios 2 and 3 with no case detection, and scenario 2b
  filter(!(Scenario %in% c("S2NoCD", "S3NoCD", "S2b"))) %>%
  # Replace S1NoCDAvg with S0
  mutate(Scenario = replace(Scenario, Scenario == "S1NoCDAvg", "S0")) %>%
  # Round columns
  mutate(CostpAgentAll = round(CostpAgentAll, 0)) %>%
  mutate(QALYpAgentAll = round(QALYpAgentAll, 3)) %>%
  mutate(ICERAdj = round(ICERAdj, 0)) %>%
  mutate(INMB = round(INMB, 0)) %>%
  # Select relevant columns
  select(Scenario, Interval, CostpAgentAll, QALYpAgentAll, ICERAdj, INMB)
# Append "_repo" to columns (except Scenario and Interval)
icol <- which(names(original_ceplane_prep) %in% c("Scenario", "Interval"))
colnames(original_ceplane_prep)[-icol] <- paste(
  colnames(original_ceplane_prep)[-icol], "repo", sep = "_")
original_ceplane_prep
```
```{r}
calc_diff_perc <- function(df, our_res, paper_res, repo_res, prefix) {
  #' Calculate the difference and percentage difference between two columns
  #' 
  #' @param df Dataframe containing columns
  #' @param our_res Column with results from our run of the model
  #' @param paper_res Column with results from the paper table 3
  #' @param repo_res Column with results from the .md files in their repository
  #' @param prefix String to prefix start of the result columns
  #' 
  #' @return Dataframe with the column pair, results, scenario and interval
  # Create column names for differences
  mydiff <- paste0(prefix, "MyDiff")
  myperc <- paste0(prefix, "MyPerc")
  repodiff <- paste0(prefix, "RepoDiff")
  repoperc <- paste0(prefix, "RepoPerc")
  # Calculate the difference and percentage difference between col1 and col2
  df %>%
    mutate(
      !!sym(mydiff) := !!sym(paper_res) - !!sym(our_res),
      !!sym(myperc) := scales::percent(round(!!sym(mydiff) / !!sym(our_res), 3)),
      !!sym(repodiff) := !!sym(paper_res) - !!sym(repo_res),
      !!sym(repoperc) := scales::percent(round(!!sym(repodiff) / !!sym(repo_res), 3))
    ) %>%
    # Select only those columns, as well as Scenario and Interval
    select(Scenario, Interval,
           !!sym(paper_res), !!sym(our_res), !!sym(repo_res),
           !!sym(mydiff), !!sym(myperc),
           !!sym(repodiff), !!sym(repoperc))
}
# Combine the model and paper results
ceplane_combine <- merge(ceplane_prep, paper_tab3_prep, by=c("Scenario", "Interval")) %>%
  merge(original_ceplane_prep, by=c("Scenario", "Interval"))
# Define the pairs of columns to compare and the prefix to use for their comparison
column_pairs <- list(
  c("CostpAgentAll", "CostpAgent_paper", "CostpAgentAll_repo", "Cost"),
  c("QALYpAgentAll", "QALYpAgent_paper", "QALYpAgentAll_repo", "QALY"),
  c("ICERAdj", "ICER_paper", "ICERAdj_repo", "ICER"),
  c("INMB", "IncrementalNMB_paper", "INMB_repo", "INMB")
)
# Combine model and paper results and apply the function for each pair of columns
ceplane_compare <- column_pairs %>%
  purrr::map(~ calc_diff_perc(ceplane_combine, .x[1], .x[2], .x[3], .x[4])) %>%
  purrr::reduce(left_join, by = c("Scenario", "Interval"))
# Remove duplicates
ceplane_compare <- ceplane_compare[!duplicated(ceplane_compare), ]
# Save to csv and view
write.csv(ceplane_compare, paths$tab3_compare, row.names=FALSE)
ceplane_compare
```

## Figure 3

```{r}
# Process data
ceplane_plot <- rbind(ceplane_3y, ceplane_5y) %>%
  # Remove scenario 2b
  filter(!(Scenario == "S2b")) %>%
  # Replace the NoCD results with a single NoCD category
  mutate(Scenario = ifelse(
    Scenario %in% c("S1NoCDAvg", "S2NoCD", "S3NoCD"), "NoCD", Scenario)) %>%
  # Add colour for S1a
  mutate(Colour = ifelse((Scenario == "S1a" & Interval == "3 years"), "A", "B"))
```

Find the efficiency frontier
```{r}
# Remove negative QALY and then...
# Find highest ICER and remove those with a QALY less than that but ICER above
find_frontier <- ceplane_plot %>%
  filter(!(IncrementalQALY <= 0)) %>%
  arrange(ICERAdj) %>%
  filter(!(IncrementalQALY <= first(IncrementalQALY) & ICERAdj > first(ICERAdj)))

# Add first row to frontier df, and remove from the other
frontier <- find_frontier[1, , drop=FALSE]
find_frontier <- find_frontier[-1,]

# Repeat that, each time adding to frontier, until there are none remaining after filter
while (nrow(find_frontier) > 0){
  find_frontier <- find_frontier %>%
    arrange(ICERAdj) %>%
    filter(!(IncrementalQALY <= first(IncrementalQALY) & ICERAdj > first(ICERAdj)))
  frontier <- rbind(frontier, find_frontier[1, , drop=FALSE])
  find_frontier <- find_frontier[-1,]
}

# Add NoCD to start of frontier
frontier <- frontier %>%
  select(Scenario, IncrementalCosts, IncrementalQALY) %>%
  add_row(Scenario="NoCD", IncrementalCosts=0, IncrementalQALY=0) %>%
  arrange(IncrementalCosts)
frontier
```

```{r, fig3}
# Create plot
ggplot(data=ceplane_plot, aes(x=IncrementalQALY, y=IncrementalCosts)) + 
  geom_point(aes(shape=factor(Interval), colour=factor(Colour))) +
  geom_text(aes(label=Scenario, colour=factor(Colour)),vjust=-0.5, size=3) + 
  geom_abline(intercept=0, slope=50000, colour="grey", linetype="dashed") +
  scale_colour_manual(values=c("red", "black")) +
  theme_bw() +
  labs(x="Incremental QALYs", y="Incremental Costs", shape="Testing Interval") +
  theme(legend.position="bottom") +
  guides(colour="none") +
  # Add the efficiency frontier
  geom_path(data=frontier, aes(x=IncrementalQALY, y=IncrementalCosts),
            colour="blue", linewidth=0.1) +
  # Extend y axis to 300 like original (but x is already wider than original)
  ylim(c(0, 300)) +
  # Make 0 to 0.015 and 0 to 300 a square
  coord_fixed(ratio = (0.015 - 0) / (300 - 0)) +
  annotate(geom="text", x = Inf, y = -Inf,
           label = "S1: All Patients\nS2: Symptomatic\nS3: Smoking History\nS1a: CDQ > 17 points",
           hjust = 1.1, vjust = -0.3, size = 2.5)

# Not needed if knitting, which will overwrite
ggsave(paths$fig3)
```

## Appendix 6

```{r appendix6}
# Create version of S1 with scenarios renamed
s1_scen <- s1 %>%
  mutate(Scenario = recode(Scenario,
                           "S1a" = "Case Detection",
                           "S1NoCDAvg" = "No Case Detection"))

ap6_df <- s1_scen %>%
  # Get the relevant scenarios
  filter(Scenario %in% c("Case Detection", "No Case Detection")) %>%
  # Adjust results so they reflect population of 1000
  mutate(across(c(Mild, Moderate, Severe, VerySevere), ~ . / (Agents/1000))) %>%
  # Tidy and make long format for plotting
  select(Scenario, Mild, Moderate, Severe, VerySevere) %>%
  tidyr::pivot_longer(cols=-Scenario, names_to="Severity", values_to="Exacerbations")

p1 <- ggplot(ap6_df, aes(x=Severity, y=Exacerbations, fill=Scenario)) +
  geom_bar(stat="identity", position="dodge") +
  labs(x="", y="Number of exacerbations", fill="") +
  theme_bw()

ap6_df <- s1_scen %>%
  # Get the relevant scenarios
  filter(Scenario %in% c("Case Detection", "No Case Detection")) %>%
  # Adjust results so they reflect population of 1000
  mutate(across(c(NoCOPD, GOLD1, GOLD2, GOLD3, GOLD4), ~ . / (Agents/1000))) %>%
  # Tidy and make long format for plotting
  select(Scenario, NoCOPD, GOLD1, GOLD2, GOLD3, GOLD4) %>%
  tidyr::pivot_longer(cols=-Scenario, names_to="Severity", values_to="Years") %>%
  # Reorder Severity to have NoCOPD first
  mutate(Severity = factor(Severity, levels = c("NoCOPD", "GOLD1", "GOLD2", "GOLD3", "GOLD4")))

p2 <- ggplot(ap6_df, aes(x=Severity, y=Years, fill=Scenario)) +
  geom_bar(stat="identity", position="dodge") +
  labs(x="", y="Patient years", fill="") +
  ylim(c(0, 15000)) +
  theme_bw()

ap6_df <- s1_scen %>%
  # Get the relevant scenarios
  filter(Scenario %in% c("Case Detection", "No Case Detection")) %>%
  # Adjust results so they reflect population of 1000
  mutate(across(c(DiagnosedPYs), ~ . / (Agents/1000)))

p3 <- ggplot(ap6_df, aes(x=Scenario, y=DiagnosedPYs, fill=Scenario)) +
  geom_bar(stat="identity", position="dodge") +
  labs(x="", y="COPD patient years diagnosed", fill="") +
  theme_bw()

ap6_df <- s1_scen %>%
  # Get the relevant scenarios
  filter(Scenario %in% c("Case Detection", "No Case Detection")) %>%
  # Adjust
  mutate(across(c(SABA, LAMA, LAMALABA, ICSLAMALABA), ~ . * 2000)) %>%
  # Tidy and make long format for plotting
  select(Scenario, SABA, LAMA, LAMALABA, ICSLAMALABA) %>%
  tidyr::pivot_longer(cols=-Scenario, names_to="Group", values_to="Years") %>%
  # Reorder group to have NoCOPD first
  mutate(Group = factor(Group, levels = c("SABA", "LAMA", "LAMALABA", "ICSLAMALABA")))

p4 <- ggplot(ap6_df, aes(x=Group, y=Years, fill=Scenario)) +
  geom_bar(stat="identity", position="dodge") +
  labs(x="", y="Patient years on treatment", fill="") +
  theme_bw()

ggarrange(p1, p2, p3, p4, ncol=2, nrow=2, common.legend = TRUE, legend="bottom")

ggsave(paths$apx6, width = 12, height = 10)
```
